The Negative Effect of Traffic Noise on House Prices: A Landscape Hedonic Analysis

### 2014-07-07 reports/NoiseHedonicRaR.Rnw
added GCVsFromMCSim figure, added captions to remaining figures in paper

\begin{figure}
\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Overview2column}}
\caption{This figure shows the spatial extent of our study area, the significant spatial variation in single family house sales prices, as well as our noise data.}\label{fig:overview}
\end{figure}

\begin{table}
\caption{Variable Description and Summary Statistics}\label{tab:sumStats}
\makebox[\linewidth][c]{
\small
\begin{tabular}{lD{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}}

 & min & 25\% & 50\% & mean & 75\% & max & st dev \\ 
  \hline
% latex table generated in R 2.15.2 by xtable 1.7-0 package
% Tue Jun 10 21:29:25 2014
Sale Price (\$1,000s) & 99 & 195 & 241 & 266 & 315 & 675 & 103 \\ 
  Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
  House Size (square feet) & 390 & 1158 & 1628 & 1750 & 2189 & 4000 & 704 \\ 
  Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
  Owner Occupancy (Yes = 1, No = 0) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
  Traffic Noise (dB) & 24.5 & 49.0 & 54.0 & 54.3 & 59.5 & 81.6 & 7.5 \\ 
  Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ 
  Distance to nearest Park (km) & 0.0 & 1.1 & 2.2 & 2.6 & 3.8 & 9.7 & 1.9 \\ 
  Distance to nearest Lake (km) & 0.0 & 0.4 & 0.8 & 0.9 & 1.3 & 4.4 & 0.7 \\ 
  Distance to nearest Shopping Center (km) & 0.0 & 0.9 & 1.5 & 1.9 & 2.3 & 10.8 & 1.6 \\ 
  Percent of Census Block Population Race = White & 0 & 80 & 90 & 85 & 96 & 100 & 17 \\ 
  Percent of Census Block Population Under Age 18 & 0 & 21 & 27 & 27 & 33 & 67 & 9 \\ 
  Median Income in Census Tract (\$1,000s) & 14 & 55 & 69 & 73 & 90 & 143 & 24 \\ 
  Elementary Test Scores & 336 & 360 & 365 & 364 & 370 & 552 & 11 \\ 
   \hline
\end{tabular}
}
\end{table}

\begin{table}
\caption{Matrix of Pearson Correlation Coefficients for Quantitative Variables}\label{tab:cor}
%\includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
\begin{center}
\small
\tabcolsep=0.05cm
\makebox[\linewidth][c]{
\begin{tabular}{l|rrrrrrrrrrrrr}
 & \multicolumn{1}{x{.35in}}{Price} & \multicolumn{1}{x{.38in}}{House} & \multicolumn{1}{x{.35in}}{Lot} & 
 \multicolumn{1}{x{.35in}}{Built} & \multicolumn{1}{x{.35in}}{Noise} & \multicolumn{1}{x{.35in}}{CBD} & \multicolumn{1}{x{.35in}}{Park} & \multicolumn{1}{x{.35in}}{Lake} & \multicolumn{1}{x{.35in}}{Shop} & \multicolumn{1}{x{.35in}}{White} & 
 \multicolumn{1}{x{.35in}}{U18} & \multicolumn{1}{x{.35in}}{Inc.} & 
 \multicolumn{1}{x{.35in}}{Test} \tabularnewline 
  \hline
Sale Price & 1 &  &  &  &  &  &  &  &  &  &  &  &  \tabularnewline
House Size & 0.74 & 1 &  &  &  &  &  &  &  &  &  &  &  \tabularnewline
Lot Size  & 0.38 & 0.45 & 1 &  &  &  &  &  &  &  &  &  &  \tabularnewline
Year Built  & 0.45 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  &  &  \tabularnewline
Noise & -0.24 & -0.12 & -0.04 & -0.25 & 1 &  &  &  &  &  &  &  &  \tabularnewline
Distance to CBD  & 0.31 & 0.45 & 0.43 & 0.58 & -0.09 & 1 &  &  &  &  &  &  &  \tabularnewline
Distance to Park  & 0.25 & 0.28 & 0.22 & 0.42 & -0.17 & 0.57 & 1 &  &  &  &  &  &  \tabularnewline
Distance to Lake & -0.04 & -0.10 & -0.25 & -0.17 & -0.01 & -0.09 & 0.20 & 1 &  &  &  &  &  \tabularnewline
Distance to Shop  & 0.27 & 0.27 & 0.15 & 0.37 & -0.24 & 0.46 & 0.38 & 0.15 & 1 &  &  &  &  \tabularnewline
Percent White & 0.24 & 0.15 & 0.25 & 0.15 & -0.09 & 0.34 & 0.16 & -0.14 & 0.14 & 1 &  &  &  \tabularnewline
Percent Under 18 & 0.26 & 0.30 & 0.11 & 0.36 & -0.19 & 0.29 & 0.32 & 0.09 & 0.32 & -0.22 & 1 &  &  \\ 
Income & 0.52 & 0.50 & 0.41 & 0.57 & -0.24 & 0.53 & 0.38 & -0.12 & 0.36 & 0.35 & 0.32 & 1 &  \tabularnewline
Elem.\ Test Scores & 0.29 & 0.28 & 0.29 & 0.34 & -0.09 & 0.35 & 0.22 & -0.10 & 0.18 & 0.31 & 0.10 & 0.44 & 1 \tabularnewline 
\end{tabular} }
\end{center} 
\end{table}

@@

\begin{figure}
\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/DensityPlotsByYear}}
\caption{This figure shows }\label{fig:DensityPlots}
\end{figure}

\begin{figure}
\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/SaleValue_with05}}
\caption{This figure shows }\label{fig:SalesYear}
\end{figure}

@@

%Table \ref{tab:LWR} summarizes the results of LWR Model (3) at three different bandwidth sizes plus the same model estimated at the ``global'' level. run without allowing for spatial variation in the regression coefficients. Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.\ 0.038) signifying a substantial improvement in model performance. In addition to the significant reduction in the GCV score obtained with the use of LWR, we also see a substantial reduction in the degree of spatial autocorrelation in the model residuals. We calculate Moran's I statistic to be 0.199 for the global model while our preferred LWR specification yields 0.012, a more than ten-fold reduction.

% Table created by stargazer v.5.1 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sat, Jun 21, 2014 - 10:37:00 AM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp]
  \caption{LWR Results: Dependent Variable = ln(Sales Price)} 
  \label{tab:LWR} 
  \makebox[\textwidth][c]{
\scriptsize
  \centering
\begin{tabular}{@{\extracolsep{-1pt}} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{3} D{.}{.}{3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex]
 & \multicolumn{3}{c}{Nearest 500 sales$^*$} & \multicolumn{3}{c}{Nearest 650 sales} & \multicolumn{3}{c}{Nearest 1000 sales} \\
 & \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
 \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
 \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$} \\
 \cline{2-4} \cline{8-10} \cline{5-7}
\multicolumn{1}{l}{Noise (dB)} & -0.0034 & -0.0064 & -0.0006 & -0.0034 & -0.0061 & -0.0009 & -0.0033 & -0.0057 & -0.0013 \\ 
\multicolumn{1}{l}{House Size (1,000s ft)} & 0.2700 & 0.1800 & 0.3900 & 0.2700 & 0.1900 & 0.3900 & 0.2700 & 0.2000 & 0.4000 \\ 
\multicolumn{1}{l}{Lot Size (acres)} & 0.4200 & 0.1700 & 0.7300 & 0.4200 & 0.1900 & 0.7100 & 0.4200 & 0.2100 & 0.6700 \\ 
\multicolumn{1}{l}{Year House Built} & 0.0046 & 0.0004 & 0.0100 & 0.0045 & 0.0005 & 0.0096 & 0.0043 & 0.0005 & 0.0090 \\ 
\multicolumn{1}{l}{Owner Occupancy} & 0.0230 & -0.0290 & 0.0800 & 0.0240 & -0.0240 & 0.0760 & 0.0230 & -0.0180 & 0.0680 \\ 
\multicolumn{1}{l}{Percent White} & 0.0012 & -0.0003 & 0.0029 & 0.0013 & -0.0001 & 0.0028 & 0.0014 & 0.0001 & 0.0028 \\ 
\multicolumn{1}{l}{Percent Under 18} & 0.0005 & -0.0016 & 0.0025 & 0.0004 & -0.0014 & 0.0022 & 0.0004 & -0.0011 & 0.0019 \\ 
\multicolumn{1}{l}{Median Income (\$1,000s)} & 0.0007 & -0.0014 & 0.0033 & 0.0008 & -0.0010 & 0.0033 & 0.0010 & -0.0006 & 0.0037 \\ 
\multicolumn{1}{l}{Elementary Test Scores} & 0.0000 & -0.0056 & 0.0055 & 0.0001 & -0.0050 & 0.0049 & 0.0003 & -0.0040 & 0.0042 \\ 
\multicolumn{1}{l}{Dist to Lake (km)} & -0.0150 & -0.0910 & 0.0580 & -0.0110 & -0.0770 & 0.0550 & -0.0076 & -0.0630 & 0.0520 \\ 
\multicolumn{1}{l}{Dist to Park (km)} & -0.0110 & -0.0600 & 0.0330 & -0.0110 & -0.0490 & 0.0250 & -0.0085 & -0.0370 & 0.0160 \\ 
\multicolumn{1}{l}{Dist to Shop (km)} & 0.0092 & -0.0330 & 0.0520 & 0.0096 & -0.0270 & 0.0470 & 0.0100 & -0.0210 & 0.0440 \\ 
\multicolumn{1}{l}{Dist to CBD (km)} & 0.0084 & -0.0190 & 0.0440 & 0.0094 & -0.0140 & 0.0400 & 0.0100 & -0.0099 & 0.0380 \\ 
\hline \\[-1.8ex] 
\multicolumn{10}{p{6 in}}{$^*$ A bandwidth of 500 implies that the nearest 500 houses sold within the past 12 months are included.} \\
\multicolumn{10}{p{6 in}}{Note: Each model also includes a categorical variable for architectural style, month*year fixed effects, and city-level fixed effects. }

\end{tabular} 
}
\end{table}

Table~\ref{tab:LWR} shows the results for our LWR Model (3) with three different bandwidths: the GCV minimizing bandwidth of 500 nearest sales as well as two larger values, 650 and 1,000 nearest sales. For each bandwidth, we display the mean LWR coefficient as well as the 10$^{th}$ and 90$^{th}$ percentile values. The mean LWR coefficient for the noise variable is similar across the three different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other varibles held constant). Unsurprisingly, the spread of the coefficient distribution is greater for the smaller bandwidths. We now turn to investigating whether this increased dispersion appears from the stochastic nature of smaller sample sizes, or due to heterogeneity in the hedonic function.

We believe the hedonic function varies significantly over space and time and that the use of a LWR estimation procedure is an appropriate and beneficial modeling strategy. In the next three subsections we describe the results of hypothesis tests that lead us to these conclusions.

>>>>

\begin{figure}
\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Overview2column}}
\caption{This figure shows the spatial extent of our study area, the significant spatial variation in single family house sales prices, as well as our noise data.}
\label{fig:overview}
\end{figure}

\begin{table}
\caption{Variable Description and Summary Statistics}
\label{tab:sumStats}
\makebox[\linewidth][c]{
\small
\begin{tabular}{lD{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}}

 & min & 25\% & 50\% & mean & 75\% & max & st dev \\ 
  \hline
% latex table generated in R 2.15.2 by xtable 1.7-0 package
% Tue Jun 10 21:29:25 2014
Sale Price (\$1,000s) & 99 & 195 & 241 & 266 & 315 & 675 & 103 \\ 
  Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
  House Size (ft$^2$) & 390 & 1158 & 1628 & 1750 & 2189 & 4000 & 704 \\ 
  Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
  Owner Occupancy (Yes = 1, No = 0) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
  Traffic Noise (dB) & 24.5 & 49.0 & 54.0 & 54.3 & 59.5 & 81.6 & 7.5 \\ 
  Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ 
  Distance to nearest Park (km) & 0.0 & 1.1 & 2.2 & 2.6 & 3.8 & 9.7 & 1.9 \\ 
  Distance to nearest Lake (km) & 0.0 & 0.4 & 0.8 & 0.9 & 1.3 & 4.4 & 0.7 \\ 
  Distance to nearest Shopping Center (km) & 0.0 & 0.9 & 1.5 & 1.9 & 2.3 & 10.8 & 1.6 \\ 
  Percent of Census Block Population Race = White & 0 & 80 & 90 & 85 & 96 & 100 & 17 \\ 
  Percent of Census Block Population Under Age 18 & 0 & 21 & 27 & 27 & 33 & 67 & 9 \\ 
  Median Income in Census Tract (\$1,000s) & 14 & 55 & 69 & 73 & 90 & 143 & 24 \\ 
  Elementary Test Scores & 336 & 360 & 365 & 364 & 370 & 552 & 11 \\ 
   \hline
\end{tabular}
}
\end{table}

\begin{table}
\caption{Matrix of Pearson Correlation Coefficients for Quantitative Variables}\label{tab:cor}
\begin{center}
\small
\tabcolsep=0.05cm
\makebox[\linewidth][c]{
\begin{tabular}{l|rrrrrrrrrrrrr}
 & \multicolumn{1}{x{.35in}}{Price} & \multicolumn{1}{x{.38in}}{House} & \multicolumn{1}{x{.35in}}{Lot} & 
 \multicolumn{1}{x{.35in}}{Built} & \multicolumn{1}{x{.35in}}{Noise} & \multicolumn{1}{x{.35in}}{CBD} & \multicolumn{1}{x{.35in}}{Park} & \multicolumn{1}{x{.35in}}{Lake} & \multicolumn{1}{x{.35in}}{Shop} & \multicolumn{1}{x{.35in}}{White} & 
 \multicolumn{1}{x{.35in}}{U18} & \multicolumn{1}{x{.35in}}{Inc.} & 
 \multicolumn{1}{x{.35in}}{Test} \tabularnewline 
  \hline
Sale Price & 1 &  &  &  &  &  &  &  &  &  &  &  &  \tabularnewline
House Size & 0.74 & 1 &  &  &  &  &  &  &  &  &  &  &  \tabularnewline
Lot Size  & 0.38 & 0.45 & 1 &  &  &  &  &  &  &  &  &  &  \tabularnewline
Year Built  & 0.45 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  &  &  \tabularnewline
Noise & -0.24 & -0.12 & -0.04 & -0.25 & 1 &  &  &  &  &  &  &  &  \tabularnewline
Distance to CBD  & 0.31 & 0.45 & 0.43 & 0.58 & -0.09 & 1 &  &  &  &  &  &  &  \tabularnewline
Distance to Park  & 0.25 & 0.28 & 0.22 & 0.42 & -0.17 & 0.57 & 1 &  &  &  &  &  &  \tabularnewline
Distance to Lake & -0.04 & -0.10 & -0.25 & -0.17 & -0.01 & -0.09 & 0.20 & 1 &  &  &  &  &  \tabularnewline
Distance to Shop  & 0.27 & 0.27 & 0.15 & 0.37 & -0.24 & 0.46 & 0.38 & 0.15 & 1 &  &  &  &  \tabularnewline
Percent White & 0.24 & 0.15 & 0.25 & 0.15 & -0.09 & 0.34 & 0.16 & -0.14 & 0.14 & 1 &  &  &  \tabularnewline
Percent Under 18 & 0.26 & 0.30 & 0.11 & 0.36 & -0.19 & 0.29 & 0.32 & 0.09 & 0.32 & -0.22 & 1 &  &  \\ 
Income & 0.52 & 0.50 & 0.41 & 0.57 & -0.24 & 0.53 & 0.38 & -0.12 & 0.36 & 0.35 & 0.32 & 1 &  \tabularnewline
Elem.\ Test Scores & 0.29 & 0.28 & 0.29 & 0.34 & -0.09 & 0.35 & 0.22 & -0.10 & 0.18 & 0.31 & 0.10 & 0.44 & 1 \tabularnewline 
\end{tabular} }
\end{center} 
\end{table}

@@

\begin{figure}
\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/DensityPlotsByYear}}
\caption{This figure shows the distribution of our variables over time. Note that there are no discernable differences in mean, standard deviation, or shape of the distribution for most variables other than sales price.}
\label{fig:DensityPlots}
\end{figure}

\begin{figure}
\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/SaleValue_with05}}
\caption{This figure shows the spatial distribution of observed sales prices over time. The change in color from 2005 to 2010 denotes the dramatic drop in sales prices associated with the recession of 2008-09. There are clear spatial patterns in  house prices that persist over time (locations with relatively high vs. low prices in one year tend to be the same in other years). However, we see no evidence that sales shifted from one area of our study region to another (neighborhoods with many sales in 2005 also tend to have many sales in 2010). }
\label{fig:SalesYear}
\end{figure}

@@

% % Table created by stargazer v.5.1 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% % Date and time: Sat, Jun 21, 2014 - 10:37:00 AM
% % Requires LaTeX packages: dcolumn 
% \begin{table}[!htbp]
%   \caption{LWR Results: Dependent Variable = ln(Sales Price)} 
%   \label{tab:LWR} 
%   \makebox[\textwidth][c]{
% \scriptsize
%   \centering
% \begin{tabular}{@{\extracolsep{-1pt}} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{3} D{.}{.}{3} } 
% \\[-1.8ex]\hline 
% \hline \\[-1.8ex]
%  & \multicolumn{3}{c}{Nearest 500 sales$^*$} & \multicolumn{3}{c}{Nearest 650 sales} & \multicolumn{3}{c}{Nearest 1000 sales} \\
%  & \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
%  \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
%  \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$} \\
%  \cline{2-4} \cline{8-10} \cline{5-7}
% \multicolumn{1}{l}{Noise (dB)} & -0.0034 & -0.0064 & -0.0006 & -0.0034 & -0.0061 & -0.0009 & -0.0033 & -0.0057 & -0.0013 \\ 
% \multicolumn{1}{l}{House Size (1,000s ft)} & 0.2700 & 0.1800 & 0.3900 & 0.2700 & 0.1900 & 0.3900 & 0.2700 & 0.2000 & 0.4000 \\ 
% \multicolumn{1}{l}{Lot Size (acres)} & 0.4200 & 0.1700 & 0.7300 & 0.4200 & 0.1900 & 0.7100 & 0.4200 & 0.2100 & 0.6700 \\ 
% \multicolumn{1}{l}{Year House Built} & 0.0046 & 0.0004 & 0.0100 & 0.0045 & 0.0005 & 0.0096 & 0.0043 & 0.0005 & 0.0090 \\ 
% \multicolumn{1}{l}{Owner Occupancy} & 0.0230 & -0.0290 & 0.0800 & 0.0240 & -0.0240 & 0.0760 & 0.0230 & -0.0180 & 0.0680 \\ 
% \multicolumn{1}{l}{Percent White} & 0.0012 & -0.0003 & 0.0029 & 0.0013 & -0.0001 & 0.0028 & 0.0014 & 0.0001 & 0.0028 \\ 
% \multicolumn{1}{l}{Percent Under 18} & 0.0005 & -0.0016 & 0.0025 & 0.0004 & -0.0014 & 0.0022 & 0.0004 & -0.0011 & 0.0019 \\ 
% \multicolumn{1}{l}{Median Income (\$1,000s)} & 0.0007 & -0.0014 & 0.0033 & 0.0008 & -0.0010 & 0.0033 & 0.0010 & -0.0006 & 0.0037 \\ 
% \multicolumn{1}{l}{Elementary Test Scores} & 0.0000 & -0.0056 & 0.0055 & 0.0001 & -0.0050 & 0.0049 & 0.0003 & -0.0040 & 0.0042 \\ 
% \multicolumn{1}{l}{Dist to Lake (km)} & -0.0150 & -0.0910 & 0.0580 & -0.0110 & -0.0770 & 0.0550 & -0.0076 & -0.0630 & 0.0520 \\ 
% \multicolumn{1}{l}{Dist to Park (km)} & -0.0110 & -0.0600 & 0.0330 & -0.0110 & -0.0490 & 0.0250 & -0.0085 & -0.0370 & 0.0160 \\ 
% \multicolumn{1}{l}{Dist to Shop (km)} & 0.0092 & -0.0330 & 0.0520 & 0.0096 & -0.0270 & 0.0470 & 0.0100 & -0.0210 & 0.0440 \\ 
% \multicolumn{1}{l}{Dist to CBD (km)} & 0.0084 & -0.0190 & 0.0440 & 0.0094 & -0.0140 & 0.0400 & 0.0100 & -0.0099 & 0.0380 \\ 
% \hline \\[-1.8ex] 
% \multicolumn{10}{p{6 in}}{$^*$ A bandwidth of 500 implies that the nearest 500 houses sold within the past 12 months are included.} \\
% \multicolumn{10}{p{6 in}}{Note: Each model also includes a categorical variable for architectural style, month*year fixed effects, and city-level fixed effects. }
% 
% \end{tabular} 
% }
% \end{table}

% Table created by stargazer v.5.1 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sat, Jul 05, 2014 - 09:41:55 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp]   
  \caption{\mbox{LWR Coefficient Mean and (10$^{th}$ to 90$^{th}$ Percentile) Values for Selected Bandwidths} }
  \label{tab:LWR} 
  \makebox[\textwidth][c]{
\scriptsize
  \centering
\begin{tabular}{@{\extracolsep{-1pt}} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
& \multicolumn{4}{c}{Dependent Variable = ln(Sales Price)} \\ \\
 & \multicolumn{1}{c}{Nearest 500$^*$ sales} & \multicolumn{1}{c}{Nearest 650 sales} & \multicolumn{1}{c}{Nearest 1,000 sales} & \multicolumn{1}{c}{Nearest 2,000 sales} \\ \hline \\
\multicolumn{1}{l}{Noise (dB)} & \multicolumn{1}{c}{-0.0034} & \multicolumn{1}{c}{-0.0034} & \multicolumn{1}{c}{-0.0033} & \multicolumn{1}{c}{-0.0032} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.0064 to -0.0007)} & \multicolumn{1}{c}{(-0.0061 to -0.0009)} & \multicolumn{1}{c}{(-0.0057 to -0.0013)} & \multicolumn{1}{c}{(-0.0049 to -0.0017)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{House Size (1,000s ft$^2$)} & \multicolumn{1}{c}{0.27} & \multicolumn{1}{c}{0.27} & \multicolumn{1}{c}{0.27} & \multicolumn{1}{c}{0.28} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.18 to 0.39)} & \multicolumn{1}{c}{(0.19 to 0.39)} & \multicolumn{1}{c}{(0.20 to 0.40)} & \multicolumn{1}{c}{(0.20 to 0.37)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Lot Size (acres)} & \multicolumn{1}{c}{0.42} & \multicolumn{1}{c}{0.42} & \multicolumn{1}{c}{0.42} & \multicolumn{1}{c}{0.40} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.17 to 0.73)} & \multicolumn{1}{c}{(0.19 to 0.71)} & \multicolumn{1}{c}{(0.21 to 0.67)} & \multicolumn{1}{c}{(0.25 to 0.58)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Year House Built} & \multicolumn{1}{c}{0.0046} & \multicolumn{1}{c}{0.0045} & \multicolumn{1}{c}{0.0043} & \multicolumn{1}{c}{0.0038} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.0004 to 0.010)} & \multicolumn{1}{c}{(0.0005 to 0.0096)} & \multicolumn{1}{c}{(0.0005 to 0.0090)} & \multicolumn{1}{c}{(0.0004 to 0.0080)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Owner Occupancy} & \multicolumn{1}{c}{0.023} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.023} & \multicolumn{1}{c}{0.021} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.029 to 0.080)} & \multicolumn{1}{c}{(-0.024 to 0.076)} & \multicolumn{1}{c}{(-0.018 to 0.068)} & \multicolumn{1}{c}{(-0.012 to 0.056)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Percent White} & \multicolumn{1}{c}{0.0012} & \multicolumn{1}{c}{0.0013} & \multicolumn{1}{c}{0.0014} & \multicolumn{1}{c}{0.0016} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.0003 to 0.0029)} & \multicolumn{1}{c}{(-0.0001 to 0.0028)} & \multicolumn{1}{c}{(0.0001 to 0.0028)} & \multicolumn{1}{c}{(0.0003 to 0.0032)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Percent Under Age 18} & \multicolumn{1}{c}{0.00047} & \multicolumn{1}{c}{0.00045} & \multicolumn{1}{c}{0.00040} & \multicolumn{1}{c}{0.00034} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.0016 to 0.0025)} & \multicolumn{1}{c}{(-0.0014 to 0.0022)} & \multicolumn{1}{c}{(-0.0011 to 0.0019)} & \multicolumn{1}{c}{(-0.0008 to 0.0015)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Median Income (\$1,000s)} & \multicolumn{1}{c}{0.0006} & \multicolumn{1}{c}{0.0008} & \multicolumn{1}{c}{0.0010} & \multicolumn{1}{c}{0.0014} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.0014 to 0.0033)} & \multicolumn{1}{c}{(-0.0010 to 0.0033)} & \multicolumn{1}{c}{(-0.0006 to 0.0037)} & \multicolumn{1}{c}{(-0.0002 to 0.0042)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Elementary Test Scores} & \multicolumn{1}{c}{-0.00002} & \multicolumn{1}{c}{0.00008} & \multicolumn{1}{c}{0.00029} & \multicolumn{1}{c}{0.00044} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.0056 to 0.0055)} & \multicolumn{1}{c}{(-0.0050 to 0.0049)} & \multicolumn{1}{c}{(-0.0040 to 0.0042)} & \multicolumn{1}{c}{(-0.0025 to 0.0037)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Distance to Lake (km)} & \multicolumn{1}{c}{-0.0150} & \multicolumn{1}{c}{-0.0110} & \multicolumn{1}{c}{-0.0076} & \multicolumn{1}{c}{-0.0051} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.091 to 0.058)} & \multicolumn{1}{c}{(-0.077 to 0.055)} & \multicolumn{1}{c}{(-0.063 to 0.052)} & \multicolumn{1}{c}{(-0.048 to 0.043)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Distance to Park (km)} & \multicolumn{1}{c}{-0.011} & \multicolumn{1}{c}{-0.011} & \multicolumn{1}{c}{-0.009} & \multicolumn{1}{c}{-0.002} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.060 to 0.033)} & \multicolumn{1}{c}{(-0.049 to 0.025)} & \multicolumn{1}{c}{(-0.037 to 0.016)} & \multicolumn{1}{c}{(-0.018 to 0.011)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Distance to Shop (km)} & \multicolumn{1}{c}{0.0092} & \multicolumn{1}{c}{0.0096} & \multicolumn{1}{c}{0.0100} & \multicolumn{1}{c}{0.0078} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.033 to 0.052)} & \multicolumn{1}{c}{(-0.027 to 0.047)} & \multicolumn{1}{c}{(-0.021 to 0.044)} & \multicolumn{1}{c}{(-0.014 to 0.036)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
\multicolumn{1}{l}{Distance to CBD (km)} & \multicolumn{1}{c}{0.0084} & \multicolumn{1}{c}{0.0094} & \multicolumn{1}{c}{0.0100} & \multicolumn{1}{c}{0.0095} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.019 to 0.044)} & \multicolumn{1}{c}{(-0.014 to 0.040)} & \multicolumn{1}{c}{(-0.010 to 0.038)} & \multicolumn{1}{c}{(-0.005 to 0.037)} \\ 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
